The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
_

Rules (5) to (8) deal with {{c1 (+) c2}} in the same way. In the case
of sums, the shape of the value {{left v}}/{{right v}} determines
whether path {{c1}} or path {{c2}} is taken. Rules (9), (10) and (11)
deal with {{c1 (*) c2}} similarly. In the case of products the value
should have the form {{(v1, v2)}} where {{v1}} flows through {{c1}}
and {{v2}} flows through {{c2}}. Both these paths are entirely
independent of each other and we could chosen to evaluate either
first, or evaluate both in parallel. In this presentation we have
chosen to follow {{c1}] first, but this choice is entirely artificial.

Finally, we end by noting the abstract machine here is interesting is
that it is a reversible machine. We could change reductions `{{|-->}}'
to run backwards `{{<--|}}', thereby computing the start state from
the stop state. We will take advantage of this property in
Sec. \ref{sec:rat}.

>>>>

Rules (5) to (8) deal with {{c1 (+) c2}} in the same way. In the case
of sums, the shape of the value,i.e. is it is tagged with {{left}} or
{{right}}, determines whether path {{c1}} or path {{c2}} is
taken. Rules (9), (10) and (11) deal with {{c1 (*) c2}} similarly. In
the case of products the value should have the form {{(v1, v2)}} where
{{v1}} flows through {{c1}} and {{v2}} flows through {{c2}}. Both
these paths are entirely independent of each other and we could
evaluate either first, or evaluate both in parallel. In this
presentation we have chosen to follow {{c1}} first, but this choice is
entirely arbitrary.

The interesting thing about the semantics is that it represents a
reversible abstract machine. In other words, we can compute the start
state from the stop state by changing the reductions `{{|-->}}' to run
backwards `{{<--|}}'. We will take advantage of this property in
Sec. \ref{sec:rat}.
